\documentclass[handout]{beamer}

\usepackage{tikz}
\usepackage{graphicx}
\usepackage{multimedia}
\usepackage[latin1]{inputenc}
\usecolortheme{lily}
\setbeamercovered{transparent}

\title[\insertdate]{Nonparametric Bayes}

\author{Omar Guti\'errez}
\institute{@omar}
\date{June 15, 2015}

\begin{document}

\begin{frame}
\titlepage
Mostly based on \textbf{A Tutorial on Bayesian Nonparametric Models} by Samuel J. Gershman.
\end{frame}

\section{The Intuition Behind}
\begin{frame}{Intuition}
    \begin{itemize}
        \item How many classes should I use in my mixture model?
        \item Learning more from the data as we see it.
        \item Parametric models...
        \item Non-parametric models have infinite number $\theta$ parameters.
        \item Examples, topics in Wikipedia, species, social networks
    \end{itemize}
\end{frame}

\section{Bayesian Inference}
\begin{frame}{Bayesian Inference}
	\begin{itemize}
        \item $P(A|D) \propto P(D|A) P(A)$
	\end{itemize}
\end{frame}

\section{Generative Model}
\begin{frame}{Generative Model}
	\begin{itemize}
        \item *
	\end{itemize}
\end{frame}

\section{Clustering}
\begin{frame}{Clustering}
	\begin{itemize}
        \item We want to get $k$ groups.
        \item We can use Gaussian Mixture Models.
        \item $ \mu_{k} \overset{iid}{\sim} \mathcal{N}(\mu, \sigma^{2}) $
        % Put an image with clusters here.
	\end{itemize}
\end{frame}

\section{Python}
\begin{frame}{Python}
	\begin{itemize}
        \item *
	\end{itemize}
\end{frame}

\section{Beta and Dirichlet Distribution}
\begin{frame}{Dirichlet Distribution}
    \begin{itemize}
        \item $\beta$ distribution.
        \item Dirichlet distribution is a generalization of $\beta$ distribution.
    \end{itemize}
\end{frame}

\section{Chinese Process Restaurant}
\begin{frame}{Chinese Process Restaurant}
    \begin{itemize}
        \item *
    \end{itemize}
\end{frame}

\begin{frame}
\huge{Thank you}\\
\huge{Questions?}\\
\end{frame}

\end{document}
